Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Minor
Table labels

Contigency table for RR mediaction. P-value for chi-squared test is
`r chisq.test(dset.species$BP_TREAT, dset.species$ANYDRUG, correct=FALSE)$p.value %>% format.pval`.

```{r self vs registered medication}
table(dset.species$BP_TREAT, dset.species$ANYDRUG) %>% kable
```

>>>>

Contigency table for RR mediaction.

```{r self vs registered medication}
tbl <- table(dset.species$BP_TREAT, dset.species$ANYDRUG)
colnames(tbl) <- c("ANYDRUG 0", "ANYDRUG 1")
rownames(tbl) <- c("BP_TREAT 0", "BP_TREAT 1")
tbl %>% kable(.)
```

\xi^2-test for medication `r format.pval(chisq.test(dset.species$BP_TREAT, dset.species$ANYDRUG, correct=FALSE)$p.value)`.
